POMDP comparisons across sigma_m, sigma_g

### 2017-12-23 appendix/appendix_harvestfirst.Rmd
harvest_first

```{r}
#B_MSY <- S_star     # recruit first, as in classic Graham-Schaefer
B_MSY <- f(S_star,0) # harvest first

@@

```{r}
meta <- expand.grid(sigma_g = c(0.02, 0.1, 0.2), 
                    sigma_m = c(0, 0.1, 0.2),
                    stringsAsFactors = FALSE) %>%
        mutate(scenario  = as.character(1:length(sigma_m)))
log_dir <- "appendix_alphas" # Store the computed solution files here
meta
```

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 10000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

Note that when recruitment happens before harvest, escapement is $f(x_t) - h_t$, not $x_t - h_t$.  The effect of a continuous function map $f$ on a discrete grid is also visible as slight wiggles.

>>>>

```{r}
#B_MSY <- S_star     # recruit first, as in classic Graham-Schaefer
B_MSY <- f(S_star,0) # harvest first, we observe the population at B_msy + h

@@

```{r}
meta <- expand.grid(sigma_g = c(0.02, 0.1, 0.15), 
                    sigma_m = c(0, 0.1, 0.15),
                    stringsAsFactors = FALSE) %>%
        mutate(scenario  = as.character(1:length(sigma_m)))
log_dir <- "appendix_alphas_harvestfirst" # Store the computed solution files here
meta
```

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 15000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@
